---
title: "Bad Boyle Data"
author: "rcj"
date: "23/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
```

## Purpose 

## Method

## Aparatus

## Observations

```{r}
bad_boyle <- readr::read_csv(here::here("data/some_bad_data.csv"))
```

We collected `r nrow(bad_boyle)` records. The graph looks like this:

```{r}
ggplot2::ggplot(data=bad_boyle)+ggplot2::geom_point(ggplot2::aes(Pressure, y=Volume), color="black")


```

Oh I might have made some mistakes. (Excellent!) Here is what I expected:

```{r}
fake_data <- tibble(x=1:20, y=12/x)

```

## Conclusions
Some of our data was very bad. We should be more careful about measurement next time. We also made typing errors in the data which we had to correct.



Let's see how our fake data maps over our real data:
```{r}
ggplot2::ggplot(data=bad_boyle)+ggplot2::geom_point(ggplot2::aes(Pressure, y=Volume))+geom_point(data=fake_data, aes(x, y), color="red")


```

