---
title: "Bad Boyle Data"
author: "rcj"
date: "23/09/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(tidyverse)
```

## Purpose 

Testing Boyle's law.

## Method


We measured pressure using a guage and volume using something else.

### Aparatus

Balloons, bike-pump, guages.

## Observations

```{r}
good_boyle <- readr::read_csv(here::here("data/good_data.csv")) 

bad_boyle <- readr::read_csv(here::here("data/bad_data.csv")) %>% 
  mutate(
    pressure = pressure+ 
                  400*(runif(nrow(good_boyle))-0.5)
    )

#boyle <- good_boyle
boyle <- bad_boyle
```

We collected `r nrow(boyle)` records. The graph looks like this:

```{r}
boyle %>% ggplot2::ggplot()+
  ggplot2::geom_point(
    ggplot2::aes(x=volume, y=pressure)
    )+
  labs(title="Pressure, what pressure?")



```

Here is a table with our data:

```{r}
DT::datatable(boyle)
```

## Conclusions
Some of our data was very bad. We should be more careful about measurement next time. We also made typing errors in the data which we had to correct.


Let's see how our fake data maps over our real data:


